Interval Probability for Fuzzy Quantum Theories

### 2016-05-29 prob.tex
prob.tex \subsection{Measuring Probabilities: Buffon's Needle Problem} Start adding the law of large numbers...

In previous section, we assume the probability of each event is known
a priori.

>>>>

In previous section, we assume the probability of each event is known
a priori. In reality, we seldom know much about events, but we assume
there is a probability behind each event, and the law of large numbers
promises us a good approximation of the probability if the experiments
run independently and identically for large enough times~\cite{Bernoulli1713,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.
